---
title: "Trends in blood pressure among blood donors"
output: 
  flexdashboard::flex_dashboard:
    theme:
      version: 5
      bg: "#2e2d2d"
      fg: "#FFFFFF"
      primary: "#333131"
      base_font:
        google: Inter Tight
      heading_font:
        google: Inter Tight
      code_font:
        google: 
          family: Inter Tight #JetBrains Mono
          local: true
    orientation: columns
    vertical_layout: fill
 # storyboard: true
    logo: "https://www.redcross.org/content/dam/redcross/imported-images/redcross-logo.png.img.png"
  lazyrmd:  
---

<style>
      .dataTables_scrollBody {
        max-height: 100% !important; /* Adjust as needed */
      }
      .chart-stage-flex {
        overflow: auto !important; /* Allows scrolling within the table container */
      }
</style>
<style type="text/css">

/* Reduce margin and padding for chart titles */
.chart-title {
  margin-top: 0;
  padding-top: 0;
}

/* Reduce padding within the overall chart container */
.flex-cell {
  padding: 5px;
}

/* Reduce space above the chart title */
.chart-title {
  margin-top: 0px; 
  padding-top: 0px;
}

/* Reduce space inside the chart box */
.flex-cell {
  padding: 2px; /* Adjust this value as needed */
}

.value-box {
    height: 91px;
    margin: 2px;
    padding: 2px;
    box-shadow: 8px 7px 4px rgba(56, 29, 29, 0.5);
    margin-bottom: 2px;
    margin-top: 2px;
    }
/* Decrease space between value and caption */
.value-box .value {
  line-height: 1;      /* Adjust the line height */
  margin-bottom: -3px; /* Move the value closer to the caption */
  font-size: 24px;
}

.value-box .caption {
  margin-top: 0;
  margin-bottom: 0;/* Remove the top margin from the caption */
}    
    
.value-box .fa {
      font-size: 8px; /* Adjust as desired */
      margin-top: 0;
      margin-bottom: -3;
    }    
    
.panel-body {
  padding: 0px !important; /* Reduce internal padding of panels */
}
.flex-panel {
  margin-bottom: 0px !important; /* Reduce vertical margin between panels */
}
.chart-container { /* Replace with actual class/ID if needed */
        margin-bottom: 0px; /* Adjust as desired */
      }

      
.graph-container {
  /* Use a linear gradient to create a shaded effect */
  background: linear-gradient(
    to bottom,
    rgba(28, 26, 26, 0.2), /* Light green, transparent */
    rgba(74, 72, 73, 0.2)  /* Light blue, transparent */
  );
  padding: 20px; /* Add padding for visual separation */
  border-radius: 8px;
}      

.value-box .icon {
  font-size:6px;
}
</style>

<style>
.crosstalk-input-slider, .irs-grid-text{
  color: white;
  font-family: Inter Tight;
  font-size:13px;
}
.irs-bar {
  background-color:black; 
}
</style>


```{css, as-is, echo=FALSE}
storyboard-nav sbframelist ul li {
    height: auto;
}

div {padding: 1 !important;}
a {
  color: lightblue; /* Change 'green' to your desired color or hex code */
}

.value-box {
  box-shadow: 0px 4px 8px rgba(0, 0, 0, 0.2);
}

.active{
      font-size:12px; /* Adjust as desired */
    }    
    
.container-fluid {
  max-width: 1000px; /* Adjust this value to your desired max-width */
}

img {
  max-width:100%;
  height: auto;
}

body {
  background: linear-gradient(to right, #636466, #2c2e30
  );
}

tags$head( 
    tags$style(HTML(".fa{font-size: 6px;}"))
  )
  
.custom-background {
  background-color: #F0F8FF; /* AliceBlue */
}  

div.blue pre { background-color:lightblue; }
div.blue pre.r { background-color:blue; }

.my_bg { background-color: rgb(245, 247, 250); color: white; border: 0px solid white; }
```


```{r libraries, include=FALSE}
library(haven)
library(dplyr)
library(gtsummary)
library(gt)
library(ggplot2)
library(freqtables)
library(huxtable)
library(lazyrmd)
library(flexdashboard)
library(crosstalk)
library(readr)
library(lubridate)
library(ggpubr)
library(RColorBrewer)
library(leaflet)
library(knitr)
library(DT)
library(plotly)
library(htmltools)
library(leaflegend)
library(ggfx)
library(ggiraph)
library(mapview)
library(tigris)
library(sf)
library(flextable)
library(downloadthis)
library(huxtable)
library(conflicted)

conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")
conflicts_prefer(plyr::mutate)

# data with highest BP status for all years ; for tables 1 and 2
setwd("E:\\ARC\\Projects\\HTN\\HTN2015data")
# htn <- read_sas("E:\\ARC\\Projects\\HTN\\HTN2015data\\htnmax1.sas7bdat") 
# demo <- read_sas("E:\\ARC\\Projects\\HTN\\HTN2015data\\demo.sas7bdat") 
htn_idlevel <- read_sas("E:\\ARC\\Projects\\HTN\\HTN2015data\\htnmax_idlevel_1.sas7bdat")
htn_idlevel <- htn_idlevel %>% mutate(Stage = case_when(stage == "1_normal"~"normal",
                                        stage == "2_elevated"~"elevated",
                                        stage == "3_stage 1"~"stage 1",
                                        stage == "4_stage 2"~"stage 2",  TRUE ~ NA)) |>
                              mutate(HBP = case_when(Stage == "normal"~"normal",
                                                     TRUE ~ "abnormal"))
htn_idlevel$Stage <- factor(htn_idlevel$Stage, levels = c("normal", "elevated", "stage 1", "stage 2"))   
htn_idlevel$HBP <- factor(htn_idlevel$HBP, levels = c("normal", "abnormal"))   
htn_idlevel$ruca <- factor(htn_idlevel$ruca, levels = c("Metropolitan", "Micro-Metropolitan", "Small Town", "Rural"))
htn_idlevel$race <- factor(htn_idlevel$race, levels = c("Black", "White", "Other"))
htn_idlevel$yr <- as.character(htn_idlevel$yr)

save(htn_idlevel, file="htn_idlevel.Rdata")
```

Column{data-width=75}
-----------------------------------------------------------------------
### Donors
```{r, fig.mobile=TRUE, class.chunk = "graph-container"}
tcount <- n_distinct(htn_idlevel$id)
    valueBox(
      value = shiny::tags$p(tcount, style = "font-size: 8px;"),
      caption = "donors age 25 & above",
      icon = tags$image('fa-users', style = "font-size: 18px;"),
      color = "#4d4c4b"
    )
```

### Donations
```{r, fig.mobile=TRUE, class.chunk = "graph-container"}
    valueBox(
      value = shiny::tags$p(20849150, style = "font-size: 8px;"),
      caption = "donations",
      icon = tags$image('fa-users', style = "font-size: 18px;"),
      color = "#4d4c4b"
    )
```

### Females
```{r, fig.mobile=TRUE, echo = FALSE}
library("shiny")
    fpercent <- htn_idlevel %>%
                group_by(gender) %>% summarise(fcount=n()) %>%
                mutate(fpercent = round(100*fcount/sum(fcount),digits = 1))
    valueBox(
          # paste0(fpercent[1,3], "%"),
          value = shiny::tags$p(paste0(fpercent[1,3], "%")),
          caption = 'females', 
          icon = 'fa-person-dress',
          color = "#C9A9A9"
    )
```

### Males
```{r, fig.mobile=TRUE, echo = FALSE}
    fpercent <- htn_idlevel %>%
                group_by(gender) %>% summarise(fcount=n()) %>%
                mutate(fpercent = round(100*fcount/sum(fcount),digits = 1))
    valueBox(
          value = shiny::tags$p(paste0(fpercent[2,3], "%"), style = "font-size: 8px; font-face:bold"),
          caption = 'males',
          # style = "font-size: 200%;font-family: Helvetica",
          icon = "fa-person",
          color = "#C1C1E8"
    )
```


### Stage 1 HTN
```{r, fig.mobile=TRUE }
stage1_ct <- htn_idlevel %>% filter(Stage == "stage 1") %>%  n_distinct()
all_ct <- n_distinct(htn_idlevel$id)
percent_st1 <- round(100*stage1_ct/all_ct, digits = 1)
    valueBox(
      paste0(percent_st1,"%"),
      caption = 'Stage 1 HTN',
      icon = 'fa-heart-circle-exclamation',
      color = "#A40"
    )
```

### Stage 2 HTN
```{r, fig.mobile=TRUE }
st2_ct <- htn_idlevel %>% filter(Stage == "stage 2") %>% n_distinct()
all_ct <- n_distinct(htn_idlevel$id)
percent_st2 <- round(100*st2_ct/all_ct, digits = 1)
    valueBox(
      paste0(percent_st2,"%"),
      caption = 'Stage 2 HTN',
      icon = 'fa-heart-circle-exclamation',
      color = "#C40000"
    )
```


Column {data-width=650 .tabset}
-----------------------------------------------------------------------
### Table 1
```{r}
table1 <- htn_idlevel |>
  select(race, gender, ages, ruca) |>
  tbl_strata(
    strata = c(race),
    .tbl_fun =
      ~ .x |>
      tbl_summary(by = gender, 
                  missing = "no", 
                  percent = "column", 
                  label = list(ruca = "RUCA", ages = "Age Group"),
                  statistic = list(
                                all_categorical() ~ "{n}/{N} ({p}%)",
                                all_continuous() ~ "{mean} ({ci})"
                                  ),
                  digits = list(all_continuous() ~ c(1, 1), all_categorical() ~ c(1,1))
                  ) |>
       add_ci(
        method = list(all_continuous() ~ "t.test", all_categorical() ~ "wilson"),
        include = everything(),
        statistic = list(all_continuous() ~ "{conf.low}, {conf.high}", 
                         all_categorical() ~ "{conf.low}%, {conf.high}%"), 
        conf.level = 0.95,
        style_fun = list(all_continuous() ~ label_style_sigfig(),
                       all_categorical() ~ label_style_sigfig(scale = 100,digits = 3) #
                         ),
        pattern = "{stat} ({ci})") |>
      modify_header(all_stat_cols() ~ "**{level}**  \nN = {n} ({style_percent(p)}%)") |> 
      # add_n() |>
      modify_spanning_header(all_stat_cols() ~ "**Race & Gender**") |>
      bold_labels() 
  ) 
table1
table1_gt <- table1 |> as_gt() 
table1_gt %>% gt::gtsave(filename = "E:/ARC/Projects/HTN/HTN2015data/donor_htn/table1.docx")

# Download button (.docx)
download_file(
  path = "E:/ARC/Projects/HTN/HTN2015data/donor_htn/table1.docx",
  output_name = "Table 1" ,
  button_label = "download table (Table 1.docx)",
  button_type = "primary",
  has_icon = TRUE,
  self_contained = TRUE
)

# Download button (.xlsx)
as_hux_xlsx(table1, file = "E:/ARC/Projects/HTN/HTN2015data/donor_htn/table1.xlsx")
download_file(
  path = "table1.xlsx",
  output_name = "Table 1" ,
  button_label = "download table (Table 1.xlsx)",
  button_type = "primary",
  has_icon = TRUE,
  self_contained = TRUE
)

table1
```

> 

### Table 2
```{r, fig.mobile=TRUE , fig.width=7.5}
table2 <- htn_idlevel |>
  select(ruca, ages, Stage) |>
  tbl_strata(
    strata = ruca,
    .tbl_fun =
      ~ .x |>
      tbl_summary(by = ages, 
                  include = c(Stage), 
                  missing = "no", 
                  percent = "column", 
                  label = list(ruca = "RUCA", agegroup = "Age Group"),
                  statistic = list(
                                all_categorical() ~ "{n}/{N} ({p}%)",
                                all_continuous() ~ "{mean} ({ci})"
                                  ),
                  digits = list(all_continuous() ~ c(1, 1), all_categorical() ~ c(2,2))
                  ) |>
      add_ci(
        method = list(all_continuous() ~ "t.test", all_categorical() ~ "wilson"),
        include = everything(),
        statistic = list(all_continuous() ~ "{conf.low}, {conf.high}", 
                         all_categorical() ~ "{conf.low}%, {conf.high}%"), 
        conf.level = 0.95,
        style_fun = list(all_continuous() ~ label_style_sigfig(),
                       all_categorical() ~ label_style_sigfig(scale = 100,digits = 4) #
                         ),
        pattern = "{stat} ({ci})") |>
      modify_header(all_stat_cols() ~ "**{level}**  \nN = {n} ({style_percent(p)}%)") |> #add_n() |> 
      # modify_spanning_header(all_stat_cols() ~ "**RUCA & Age Group**") |>
      bold_labels() 
  ) 

gt_obj_1 <- table2 %>% as_gt()
# gt_obj_2 <- table3 %>% as_gt()
# table2 <- gt::gt_group(gt_obj_1, gt_obj_2)
gt_obj_1 %>% gt::gtsave(filename = "table2.docx")
download_file(
  path = "E:/ARC/Projects/HTN/HTN2015data/donor_htn/table2.docx",
  output_name = "Table 2" ,
  button_label = "download (Table 2 Word)",
  button_type = "primary",
  has_icon = TRUE,
  self_contained = TRUE
)

# table2 %>% as_gt() %>% gt::gtsave(filename = "table2.docx")
# This will save the table as an Excel file with the specified name
as_hux_xlsx(table2, file = "E:/ARC/Projects/HTN/HTN2015data/donor_htn/table2.xlsx")
# as_hux_xlsx(table2b, file = "E:/ARC/Projects/HTN/HTN2015data/donor_htn/table2b.xlsx")

download_file(
  path = "table2.xlsx",
  output_name = "Table 2" ,
  button_label = "download (Table 2 Excel)",
  button_type = "primary",
  has_icon = TRUE,
  self_contained = TRUE
)
download_file(
  path = "table2.xlsx",
  output_name = "Table 2" ,
  button_label = "download (Table 2 Excel)",
  button_type = "primary",
  has_icon = TRUE,
  self_contained = TRUE
)

table2
```


### Table 3
```{r, fig.mobile=TRUE , fig.width=7.5}
table3 <- htn_idlevel |>
  select(Stage, gender, race) |>
  tbl_strata(
    strata = race,
    .tbl_fun =
      ~ .x |>
      tbl_summary(by = gender,  
                  include = c(Stage), 
                  missing = "no", 
                  percent = "column", 
                  label = list(race = "Race", gender = "Gender"),
                  statistic = list(
                                all_categorical() ~ "{n}/{N} ({p}%)",
                                all_continuous() ~ "{mean} ({ci})"
                                  ),
                  digits = list(all_continuous() ~ c(1, 1), all_categorical() ~ c(2,2))
                  ) |>
      add_ci(
        method = list(all_continuous() ~ "t.test", all_categorical() ~ "wilson"),
        include = everything(),
        statistic = list(all_continuous() ~ "{conf.low}, {conf.high}", 
                         all_categorical() ~ "{conf.low}%, {conf.high}%"), 
        conf.level = 0.95,
        style_fun = list(all_continuous() ~ label_style_sigfig(),
                       all_categorical() ~ label_style_sigfig(scale = 100,digits = 4) #
                         ),
        pattern = "{stat} ({ci})") |>
      modify_header(all_stat_cols() ~ "**{level}**  \nN = {n} ({style_percent(p)}%)") |> #add_n() |> 
      # modify_spanning_header(all_stat_cols() ~ "**Race & Gender**") |>
      bold_labels() 
  ) 

# gt_obj_1 <- table2 %>% as_gt()
gt_obj_3 <- table3 %>% as_gt()
# table2 <- gt::gt_group(gt_obj_1, gt_obj_2) 
gt_obj_3 %>% gt::gtsave(filename = "table3.docx")
download_file(
  path = "E:/ARC/Projects/HTN/HTN2015data/donor_htn/table3.docx",
  output_name = "Table 3" ,
  button_label = "download (Table 3 Word)",
  button_type = "primary",
  has_icon = TRUE,
  self_contained = TRUE
)

# table2 %>% as_gt() %>% gt::gtsave(filename = "table2.docx")
# This will save the table as an Excel file with the specified name
as_hux_xlsx(table3, file = "E:/ARC/Projects/HTN/HTN2015data/donor_htn/table3.xlsx")

download_file(
  path = "table3.xlsx",
  output_name = "Table 3" ,
  button_label = "download (Table 3 Excel)",
  button_type = "primary",
  has_icon = TRUE,
  self_contained = TRUE
)

table3
```


### Race 
```{r, fig.mobile=TRUE , fig.width=7.5}
# Race
htn_idlevel %>% 
  freq_table(race) %>% 
  select(cat, n, n_total, percent, lcl, ucl) %>% 
  mutate(percent = round(percent, digits = 2),
         lcl = round(lcl, digits = 2),
         ucl = round(ucl, digits = 2)
         ) %>%
  rename("race" = "cat",
         "total donors" = "n_total"
         ) %>% 
  as_gtsummary()
```

### Age 
```{r, fig.mobile=TRUE , fig.width=7.5}
htn_idlevel %>% 
  freq_table(ages) %>%
  freq_format( recipe = "percent (lcl- ucl)", name = "percent_95", digits = 2 ) %>%
  select(cat, n, percent_95) %>% 
  rename("Age" = "cat",
         "donors" = "n",
         "percent (95 CI)" = "percent_95"
         ) %>% 
  as_gtsummary()
```

### RUCA 
```{r, fig.mobile=TRUE , fig.width=7.5}
htn_idlevel %>% 
  freq_table(ruca) %>% 
  select(cat, n, n_total, percent, se) %>% 
  mutate(percent = round(percent, digits = 2),
         se = round(se, digits = 2)) %>%
  rename("RUCA" = "cat",
         "total donors" = "n_total"
         ) %>% 
  as_gtsummary()
```


### Stages 
```{r, fig.mobile=TRUE , fig.width=7.5}
htn_idlevel %>% 
  freq_table(Stage) %>%
  freq_format( recipe = "percent (lcl- ucl)", name = "percent_95", digits = 2 ) %>%
  select(cat, n, percent_95) %>% 
  rename("Stage" = "cat",
         "donors" = "n",
         "percent (95 CI)" = "percent_95"
         ) %>% 
  as_gtsummary()
```


### RUCA & Stages 
```{r, fig.mobile=TRUE , fig.width=7.5}
htn_idlevel %>% 
  freq_table(ruca, HBP) %>%
  freq_format( recipe = "percent_row (lcl_row - ucl_row)", name = "percent (95 CL)", digits = 2 ) %>%
  select(row_cat, col_cat, n, `percent (95 CL)`) %>% 
  rename(
    "RUCA" = "row_cat",
    "HBP" = "col_cat",
    "donors" = "n"
         ) %>% 
  as_gtsummary() %>% as_gt() %>%
      tab_style(
        style = list(cell_fill(color = "lightblue")),
        locations = cells_body(rows = c(1,2,3,4,9,10)) # Colors rows 1 and 3
      ) 
      # tab_style(
      #   style = list(cell_fill(color = "gray")),
      #   locations = cells_body(rows = Stage == "stage 2") # Colors rows where 'variable' column is "age"
      # )
```


### Age & Stages 
```{r, fig.mobile=TRUE , fig.width=7.5}
htn_idlevel %>% 
  freq_table(ages, Stage) %>%
  freq_format( recipe = "percent_row (lcl_row - ucl_row)", name = "percent (95 CL)", digits = 2 ) %>%
  select(row_cat, col_cat, n, `percent (95 CL)`) %>% 
  rename(
    "Age" = "row_cat",
    "Stage" = "col_cat",
    "donors" = "n"
         ) %>% 
  as_gtsummary() %>% as_gt() %>%
      tab_style(
        style = list(cell_fill(color = "lightblue")),
        locations = cells_body(rows = c(1,2,3,4)) # Colors rows 1 and 3
      ) 
      # tab_style(
      #   style = list(cell_fill(color = "gray")),
      #   locations = cells_body(rows = Stage == "stage 2") # Colors rows where 'variable' column is "age"
      # )
```


### Age & HBP 
```{r, fig.mobile=TRUE , fig.width=7.5}
htn_idlevel %>% 
  freq_table(ages, HBP) %>%
  freq_format( recipe = "percent_row (lcl_row - ucl_row)", name = "percent (95 CL)", digits = 2 ) %>%
  select(row_cat, col_cat, n, `percent (95 CL)`) %>% 
  rename(
    "Age" = "row_cat",
    "HBP" = "col_cat",
    "donors" = "n"
         ) %>% 
  as_gtsummary() %>% as_gt() %>%
      tab_style(
        style = list(cell_fill(color = "lightblue")),
        locations = cells_body(rows = c(1,2,3,4)) # Colors rows 1 and 3
      ) 
      # tab_style(
      #   style = list(cell_fill(color = "gray")),
      #   locations = cells_body(rows = Stage == "stage 2") # Colors rows where 'variable' column is "age"
      # )
```


### Gender & Stages 
```{r, fig.mobile=TRUE , fig.width=7.5}
htn_idlevel %>% 
  freq_table(gender, HBP) %>%
  freq_format( recipe = "percent_row (lcl_row - ucl_row)", name = "percent (95 CL)", digits = 2 ) %>%
  select(row_cat, col_cat, n, `percent (95 CL)`) %>% 
  rename(
    "Gender" = "row_cat",
    "HBP" = "col_cat",
    "donors" = "n"
         ) %>% 
  as_gtsummary() %>% as_gt() %>%
      tab_style(
        style = list(cell_fill(color = "lightblue")),
        locations = cells_body(rows = c(2,4)) # Colors rows 1 and 3
      ) 
      # tab_style(
      #   style = list(cell_fill(color = "gray")),
      #   locations = cells_body(rows = Stage == "stage 2") # Colors rows where 'variable' column is "age"
      # )
```


### Race & Stages 
```{r, fig.mobile=TRUE , fig.width=7.5}
htn_idlevel %>% 
  freq_table(race, HBP) %>%
  freq_format( recipe = "percent_row (lcl_row - ucl_row)", name = "percent (95 CL)", digits = 2 ) %>%
  select(row_cat, col_cat, n, `percent (95 CL)`) %>% 
  rename(
    "Race" = "row_cat",
    "HBP" = "col_cat",
    "donors" = "n"
         ) %>% 
  as_gtsummary() %>% as_gt() %>%
      tab_style(
        style = list(cell_fill(color = "lightblue")),
        locations = cells_body(rows = c(2,4,6)) # Colors rows 1 and 3
      ) 
      # tab_style(
      #   style = list(cell_fill(color = "gray")),
      #   locations = cells_body(rows = Stage == "stage 2") # Colors rows where 'variable' column is "age"
      # )
```


